### 2011-05-10 paper.tex
Added two operator definitions

\newcommand{\bp}{\textsf{BP}}
\newcommand{\strongbp}{\widehat{\textsf{BP}}}
%\newcommand{\strongbp}{\textsf{strongBP}}
\newcommand{\bpp}{\textsf{BPP}}
\newcommand{\parity}{\oplus}
\newcommand{\p}{\textsf{P}}
\newcommand{\op}{\textsf{Op}}
\newcommand{\pp}{\textsf{PP}}
\newcommand{\x}{\textsf{X}}
\newcommand{\intersection}{\textsf{intersect}}
\newcommand{\intersect}{\textsf{intersect}}
\newcommand{\majority}{\textsf{majority}}

@@

@@

\begin{theorem}\label{amplify}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. Then \emph{$\bp \cdot C = \strongbp \cdot C$}.
\end{theorem}
Initially, this may seem to be obviously true for the same reasons that $\bp \cdot \p = \strongbp \cdot \bp$. The problem is that amplification requires running some machine which accepts a language in $C$ more than once. This requires the structure of $C$ to allow for such repetitions. This brings us to the concept of majority reductions.
\begin{definition}\label{defmajority}\emph{
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any language $L$, the language $\majority(L) = \{(x_1,...,x_k) : k \in \mathbb{N}, |\{x_i : x_i \in L\}| \ge k/2\}$ is in $C$.
}\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions, then\linebreak \emph{$\bp \cdot C = \strongbp \cdot C$.}
\end{lemma}
\begin{proof}
This is now the same application of the Chernoff bound which shows that $\bp \cdot \p = \strongbp \cdot \p$. Suppose $L$ is a language in $\bp \cdot C$. Then there is a language $M$ in $C$ such that $\pr_y [(x,y) \in M] > 2/3$ if $x\in L$ and $\pr_y [(x,y)\in M] < 1/3$ if $x\not\in L$, where the length of $y$ is polynomial in the length of $x$. Let $q$ be a polynomial, where $e^{-q(|x|)}$ is the desired error probability. Let $k = 48q(|x|)$.

Here is how we determine if a string $x$ is in $L$ with error probability $e^{-q(|x|)}$. Choose $k$ strings $y_1,y_2,...,y_k$ randomly. Then accept if a majority of $(x,y_1),(x,y_2),...,(x,y_k)$ are in $M$, which is possible to do since $\majority(M) \in C$. Let $X_i$ be an indicator variable which is $1$ if $(x,y_i)$ is in $M$. Then by the Chernoff bound,
\begin{align*}
\pr\left[\sum X_i < k/2\right] &= \pr\left[\sum X_i < (1 - 1/4)(2k/3)\right]\\
&< e^{-(1/4)^2 (2k/3) / 2}\\
&= e^{-q(|x|)}
\end{align*}
We can do this for any polynomial $q$, so $L \in \strongbp \cdot C$. Hence, $\bp \cdot C = \strongbp \cdot C$.
\end{proof}

Thus, in order to prove Theorem \ref{amplify}, we just need to show that any \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class is closed under majority reductions. In order to show that these are closed under majority reductions, we will need the help of another property:
\begin{definition}\label{defintersection}
We say that a class $C$ is \emph{closed under intersection} if for any language $L \in C$, the language $\intersection(L) = \{(x_1,...,x_k) : k\in\mathbb{N}, x_i \in L_i ~ \forall i\}$ is in $C$.
\end{definition}
We will demonstrate that all $\{\Sigma, \Pi, \bp, \parity\}$-constructible complexity classes are closed under intersection and under majority reductions. To do this, we will use induction on the number of operators in $C$. Clearly $\p$ is closed under intersection and majority reductions. Thus, the result follows from the following two lemmas:

@@

>>>>

\newcommand{\bp}{\textsf{BP}}
\newcommand{\strongbp}{\widehat{\textsf{BP}}}
%\newcommand{\strongbp}{\textsf{strongBP}}
\newcommand{\bpp}{\textsf{BPP}}
\newcommand{\parity}{\oplus}
\newcommand{\p}{\textsf{P}}
\newcommand{\op}{\textsf{Op}}
\newcommand{\pp}{\textsf{PP}}
\newcommand{\np}{\textsf{NP}}
\newcommand{\conp}{\textsf{coNP}}
\newcommand{\x}{\textsf{X}}
\newcommand{\intersection}{\textsf{intersect}}
\newcommand{\intersect}{\textsf{intersect}}
\newcommand{\majority}{\textsf{majority}}

@@

In this paper we focus on four operators on complexity classes: $\Sigma, \Pi, \bp, \parity$ which are defined in analogy to the relationship between $\p$ and the classes $\np$, $\conp$, $\bpp$, and $\parity\p$. For all of these definitions, we let $\langle x, y\rangle$ denote a single string of size $O(|x| + |y|)$ that represents the pair $(x,y)$.

\begin{definition}\label{opsigma}
For a complexity class $C$, we define the class $\Sigma \cdot C$ as the set of partial functions $f$ such that there exists a partial function $g \in C$ and a polynomial $p(n)$ such that
\begin{itemize}
\item $f(x) = 1$ if and only if there exists a $y \in \{0,1\}^{p(|x|)}$ such that $g(\langle x,y \rangle) = 1$.
\item $f(x) = 0$ if and only if for every $y \in \{0,1\}^{p(|x|)}$, we have $g(\langle x, y\rangle) = 0$.
\item $f(x) = \x$ otherwise.
\end{itemize}
\end{definition}

\begin{definition}\label{oppi}
For a complexity class $C$, we define the class $\Pi \cdot C$ as the set of partial functions $f$ such that there exists a partial function $g \in C$ and a polynomial $p(n)$ such that
\begin{itemize}
\item $f(x) = 1$ if and only if for every $y \in \{0,1\}^{p(|x|)}$, we have $g(\langle x,y \rangle) = 1$.
\item $f(x) = 0$ if and only if there exists $y \in \{0,1\}^{p(|x|)}$ such that $g(\langle x, y\rangle) = 0$.
\item $f(x) = \x$ otherwise.
\end{itemize}
\end{definition}

@@

\begin{theorem}\label{amplify}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. Then \emph{$\bp \cdot C = \strongbp \cdot C$}.
\end{theorem}
Initially, this may seem to be obviously true for the same reasons that $\bp \cdot \p = \strongbp \cdot \bp$. The problem is that amplification requires running some machine which accepts a language in $C$ more than once. This requires the structure of $C$ to allow for such repetitions. This brings us to the concept of majority reductions.
\begin{definition}\label{defmajority}\emph{
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any language $L$, the language $\majority(L) = \{(x_1,...,x_k) : k \in \mathbb{N}, |\{x_i : x_i \in L\}| \ge k/2\}$ is in $C$.
}\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions, then\linebreak \emph{$\bp \cdot C = \strongbp \cdot C$.}
\end{lemma}
\begin{proof} \end{proof}
Thus, in order to prove Theorem \ref{amplify}, we just need to show that any \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class is closed under majority reductions. In order to show that these are closed under majority reductions, we will need the help of another property:
\begin{definition}\label{defintersection}
We say that a class $C$ is \emph{closed under intersection} if for any language $L \in C$, the language $\intersection(L) = \{(x_1,...,x_k) : k\in\mathbb{N}, x_i \in L_i ~ \forall i\}$ is in $C$.
\end{definition}
We will demonstrate that all $\{\Sigma, \Pi, \bp, \parity\}$-constructible complexity classes are closed under intersection and under majority reductions. To do this, we will use induction on the number of operators in $C$. Clearly $\p$ is closed under intersection and majority reductions. Thus, the result follows from the following two lemmas:

@@

\bibitem{Schoning} Sch\"oning, U. \emph{Probabilitistic complexity classes and lowness}, Proceedings of the 2nd IEEE Conference on Structure in Complexity Theory, 1987, pp. 2-8.

\bibitem{Schoning2} Sch\"oning, U. \emph{The power of counting}, Proceedings of the 3rd IEEE Conference on Structure in Complexity Theory, 1988, pp. 2-9.
